Improved Approximation Algorithms for the Maximum Carpool Matching Problme

### 2017-02-13 src/appendix.tex
fix figs

\section{Omitted Proof}

\begin{proof}[Proof of Theorem~\ref{thm:improve}]
Define the weight function $w'(e)
= \floor{\frac{w(e)}{w_{\max}} \cdot \frac{m}{2\eps}}$, where
$w_{\max} \eqdf \max_{e \in A} w(v)$.
%
Let $M^*$ and $M'$ be an optimal carpool matchings with respect to $w$
and $w'$, resp.  We have that
\[
w'(M^*)
=    \sum_{e \in M^*} \floor{\frac{w(e)}{w_{\max}} \cdot \frac{m}{2\eps}}
>    \sum_{e \in M^*} \paren{ \frac{w(e)}{w_{\max}} \cdot \frac{m}{2\eps} } - m
=    \frac{m}{2\eps w_{\max}} \cdot w(M^*) - m
~.
\]
Since $w(M^*) \geq w_{\max}$, we have that 
\[
w'(M^*)
>    \frac{m}{2\eps w_{\max}} \cdot (w(M^*) - 2\eps w_{\max})
\geq \frac{m}{2\eps w_{\max}} \cdot (1 - 2\eps) w(M^*)
~.
\]
By Theorem~\ref{thm:improve-bounded}, our local improvement algorithm computes a
$\half$-approximate carpool matching $M$ on $(G, c, w')$, and this
matching satisfies $w'(M) \geq w'(M')/2$.  Furthermore, since
$w'(M') \geq w'(M^*)$, it follows that $w'(M) \geq w'(M^*)/2$.
Therefore
\[
w(M)
\geq \frac{2\eps w_{\max}}{m} w'(M) 
\geq \frac{1}{2} \frac{2\eps w_{\max}}{m} w'(M^*)
>    \frac{1-2\eps}{2} w(M^*)
~,
\]
as required.
\end{proof}

>>>>

\section{Omitted Proof}
\begin{proof}[Proof of Theorem~\ref{thm:improve}]
Define the weight function $w'(e)
= \floor{\frac{w(e)}{w_{\max}} \cdot \frac{m}{2\eps}}$, where
$w_{\max} \eqdf \max_{e \in A} w(v)$.
%
Let $M^*$ and $M'$ be an optimal carpool matchings with respect to $w$
and $w'$, resp.  We have that
\[
w'(M^*)
=    \sum_{e \in M^*} \floor{\frac{w(e)}{w_{\max}} \cdot \frac{m}{2\eps}}
>    \sum_{e \in M^*} \paren{ \frac{w(e)}{w_{\max}} \cdot \frac{m}{2\eps} } - m
=    \frac{m}{2\eps w_{\max}} \cdot w(M^*) - m
~.
\]
Since $w(M^*) \geq w_{\max}$, we have that 
\[
w'(M^*)
>    \frac{m}{2\eps w_{\max}} \cdot (w(M^*) - 2\eps w_{\max})
\geq \frac{m}{2\eps w_{\max}} \cdot (1 - 2\eps) w(M^*)
~.
\]
By Theorem~\ref{thm:improve-bounded}, our local improvement algorithm computes a
$\half$-approximate carpool matching $M$ on $(G, c, w')$, and this
matching satisfies $w'(M) \geq w'(M')/2$.  Furthermore, since
$w'(M') \geq w'(M^*)$, it follows that $w'(M) \geq w'(M^*)/2$.
Therefore
\[
w(M)
\geq \frac{2\eps w_{\max}}{m} w'(M) 
\geq \frac{1}{2} \frac{2\eps w_{\max}}{m} w'(M^*)
>    \frac{1-2\eps}{2} w(M^*)
~,
\]
as required.
\end{proof}

\section{Tight Analysis}
We now show that Corollary~\ref{cor:local} is tight.  Consider the
example in Figure~\ref{fig:local search tight}, the example is for the
special case when $k = 11$ and $\cmax = 2$ but this example can be
generalized in a straightforward manner.  One can verify that as the
graph in the example growth, the ratio between the optimal solution
and the local search solution approaches $\frac{3}{4}$.

\begin{figure}
\begin{center}
\scalebox{.85}{\input{fig-local-tight}}
\caption{A tight example for Corollary~\ref{cor:local}. 
The optimal solution is given by the red solid arcs while the local
search solution is given by the green, dashed arcs.  The solution can
be improved by the local search algorithm only if it removes all the
edges.}
\label{fig:local search tight}
\end{center}
\end{figure}

### 2017-02-13 src/in/tikz.tex
Merge Dror
fix
fix figs

\usepackage{tikz}
\usetikzlibrary{
	arrows,
	arrows.meta,
	calc,
	graphs,
	patterns,
	positioning,
	shapes,
	decorations.pathmorphing,
	math,
}

%DEFAULT STYLE
\tikzset{default style/.style={
	>=Stealth, 
	on grid, 
	auto, 
	thick,
}}

% NODE
\tikzset{default node/.style={
	draw, 
	circle,
	inner sep=0mm,
	minimum size=5mm,
	very thick,
	font=\small,
	black!70,
}}

% LABELS
\tikzset{label/.style={
	draw=none,
	sloped,
}}

\tikzset{label above/.style={
	label,
	midway,
	above=-1mm,
}}

\tikzset{label below/.style={
	label,
	midway,
	below=-1mm,
}}

>>>>

\usepackage{tikz}
\usetikzlibrary{
	arrows.meta,
	calc,
	graphs,
	patterns,
	positioning,
	shapes,
	decorations.pathmorphing,
	math,
}

% NODE
\tikzset{default node/.style={draw,circle,inner sep=0mm,minimum size=5mm,very thick,font=\small,black!70,}}

% LABELS
\tikzset{label/.style={draw=none,sloped,}}
\tikzset{label above/.style={label,midway,above=-1mm,}}
\tikzset{label below/.style={label,midway,below=-1mm,}}
\tikzset{outline/.style={loosely dashed, ultra thin, lightgray}}
\tikzset{m/.style={blue, dashed}}

%DEFAULT STYLE
\tikzset{
	>=Triangle[], 
	on grid, 
	auto, 
	thick,
}

### 2017-02-13 src/local.tex
fix figs

To analyze the approximation ratio achieved by the local search
algorithm consider an arbitrary but fixed optimal matching $M^*$.
Given the solution outputted by the local search algorithm, $M$, we
build the \emph{star graph} of the two solutions in which each node
represents a star from the optimal solution, namely from $\calS(M^*)$,
and an edge exists between two nodes if there is a star in $\calS(M)$
that intersects the two corresponding stars of the optimal solution.
%
Formally $H = (\calS(M^*), E)$ where
\[
E = \set{(S^*_i, S^*_j) : \exists S \in \calS(M), 
         V(S) \cap V(S^*_i) \neq \emptyset \land
         V(S) \cap V(S^*_j) \neq \emptyset}
~.
\]
Figure~\ref{fig:conflict} depicts a star graph.

\begin{figure}[t]
%
\begin{subfigure}{.4\linewidth}
\caption{\label{subfloat:graph}}
\input{fig-sub-graph}
\end{subfigure}
%
\hfill
%
\begin{subfigure}{.4\linewidth}
\caption{\label{subfloat:conflict}}
\input{fig-sub-conflict}
\end{subfigure}
%
\caption[]{
\subref{subfloat:graph} 
An optimal matching depicted by the dashed red edges,
and another solution depicted by the solid green edges.  
\subref{subfloat:conflict}
The conflict graph, the upper left vertex corresponds 
to the star that contains the vertices a,b,c.
The numbers inside the vertices corresponds to $d_i$.   
}
\label{fig:conflict}
\end{figure}

@@

We now show that Corollary~\ref{cor:local} is tight.  Consider the
example in Figure~\ref{fig:local search tight}, the example is for the
special case when $k = 11$ and $\cmax = 2$ but this example can be
generalized in a straightforward manner.  One can verify that as the
graph in the example growth, the ratio between the optimal solution
and the local search solution approaches $\frac{3}{4}$.

\begin{figure}
\begin{center}
\input{fig-local-tight}
\caption{A tight example for Corollary~\ref{cor:local}. 
The optimal solution is given by the red solid arcs while the local
search solution is given by the green, dashed arcs.  The solution can
be improved by the local search algorithm only if it removes all the
edges.}
\label{fig:local search tight}
\end{center}
\end{figure}

>>>>

To analyze the approximation ratio achieved by the local search
algorithm consider an arbitrary but fixed optimal matching $M^*$.
Given the solution outputted by the local search algorithm, $M$, we
build the \emph{star graph} of the two solutions in which each node
represents a star from the optimal solution, namely from $\calS(M^*)$,
and an edge exists between two nodes if there is a star in $\calS(M)$
that intersects the two corresponding stars of the optimal solution.
%
Formally $H = (\calS(M^*), E)$ where
$
{E = \set{(S^*_i, S^*_j) : \exists S \in \calS(M), 
         V(S) \cap V(S^*_i) \neq \emptyset \land
         V(S) \cap V(S^*_j) \neq \emptyset}}
$.
Figure~\ref{fig:conflict} depicts a star graph.

\begin{figure}[t]
%
\begin{subfigure}[t]{.4\linewidth}
\caption{\label{subfloat:graph}}
\input{fig-sub-graph}
\end{subfigure}
%
\hfill
%
\begin{subfigure}[t]{.4\linewidth}
\caption{\label{subfloat:conflict}}
\input{fig-sub-conflict}
\end{subfigure}
%
\caption[]{
\subref{subfloat:graph} 
An optimal matching depicted by the dashed red edges,
and another solution depicted by the solid green edges.
The optimal stars are outlined.  
\subref{subfloat:conflict}
The star graph, each vertex corresponded to a star in the original graph. 
The upper left vertex corresponds to the star that contains the vertices a,b,c.
The numbers inside the vertices corresponds to $d_i$.   
}
\label{fig:conflict}
\end{figure}

@@

In the appendix we show that our analysis is tight.
